### 2014-04-12 paper/designspace.tex
bjoern's pass

\emph{Open} pipes may be used to create electronic circuitry.  For example, an open pipe filled with conductive paint and connected to a battery can provide power to an LED (see Figure \ref{fig:openings}a).
%
\emph{Semi-enclosed} pipes are capped on one side and could be used to create create tactile output. By fabricating a cap from a malleable material and attaching a pump to the open end, haptic feedback can be generated by raising and depressing the flexible cap (see Figure \ref{fig:openings}c).
%
\emph{Fully enclosed} pipes (cavities) are entirely internal to the object.  Fully enclosed pipes may be used as weight modifiers~\cite{Prevost-makeitstand} and for object identification~\cite{Willis-infrastructs}, as in Figure \ref{fig:openings}d.  If printed in parts and assembled post-print, enclosed pipes could also contain water or particles that would otherwise fall out.

\subsection{Path Constraints}
Depending on the purpose of the pipe, its geometry may be constrained to specific locations within the 3D model. An \emph{endpoint-constrained} pipe requires specific start and end points, but the particular route of the internal path is irrelevant. This is the case for circuit schematics, where the electronic components have a fixed location, but many routing solutions are valid. In contrast, for a \emph{path-constrained} pipe the shape of the path is important. For example, threading electroluminescent (EL) wire through a clear pipe enables makers to emulate neon art (see Figure \ref{fig:openings}b). A \emph{fully constrained} pipe requires both specific terminals as well as a specific path. If a maker wishes the EL wire to exit the rear of the sign to hide the electronics, it requires a fully-constrained path (Figure \ref{fig:neon}). Finally, an \emph{unconstrained} pipe does not need a specific path or terminal points. A cavity to modify an object's weight is an example of an unconstrained pipe.

>>>>

\emph{Open} pipes may be used to create electronic circuitry.  For example, an open pipe filled with conductive paint and connected to a battery can provide power to an LED (see Figure \ref{fig:openings}a).
%
\emph{Semi-enclosed} pipes are capped on one side and could be used to create create tactile output. By fabricating a cap from a malleable material and attaching a pump to the open end, haptic feedback can be generated by raising and depressing the flexible cap (see Figure \ref{fig:openings}b).
%
\emph{Fully enclosed} pipes (cavities) are entirely internal to the object.  Fully enclosed pipes may be used as weight modifiers~\cite{Prevost-makeitstand} and for object identification~\cite{Willis-infrastructs}, as in Figure \ref{fig:openings}c.  If printed in parts and assembled post-print, enclosed pipes could also contain water or particles that would otherwise fall out.

\subsection{Path Constraints}
Depending on the purpose of the pipe, its geometry may be constrained to specific locations within the 3D model. An \emph{endpoint-constrained} pipe requires specific start and end points, but the particular route of the internal path is flexible. This is the case for circuit schematics, where the electronic components have a fixed location, but many routing solutions are valid. In contrast, for a \emph{path-constrained} pipe the shape of the path is important. For example, threading electroluminescent (EL) wire through a clear pipe enables makers to emulate neon art (see Figure \ref{fig:openings}b) \bjoern{what happened to this subfigure? Kill reference if it's not coming back}. A \emph{fully constrained} pipe requires both specific terminals as well as a specific path. If a maker wishes the EL wire to exit the rear of the sign to hide the electronics, it requires a fully-constrained path (Figure \ref{fig:neon}). Finally, an \emph{unconstrained} pipe does not need a specific path or terminal points. A cavity to modify an object's weight is an example of an unconstrained pipe.

### 2014-04-12 paper/discussion.tex
bjoern's pass

The promise of 3D printing is two-fold: it enables the manufacturing of complex objects at low volumes, and it allows for the manufacturing of geometries that are impossible to create using traditional techniques like injection molding.  Printing pipes to prototype interactive objects exploits both advantages. Prototypes by definition are low-volume parts, and pipes require complex interior geometries that are very difficult or impossible to produce using other processes. Our work has focused on routing pipes that are manually filled after a print has completed. However, the fundamental operations of 3D path routing and topology specification that our tool offers will remain relevant as 3D printing technology advances. Multi-material printers are already available; as they advance and support the embedding of additional materials (e.g., conductive), \systemname can enable designers to efficiently specify where different functional materials should be placed at design time.

@@

\emph{Aural} outputs can be created with gases.  Pipes and cavities can act as resonators can be leveraged to create 3D-printed sound chambers with explicitly designed sound characteristics~\cite{Zoran-flute} (see Figure \ref{fig:speculative}a).  %All that is necessary for this is an enclosed chamber with a pipe connected to it via a narrow neck-point (see Figure \ref{fig:ocarina}).  
Passive sound amplification and sound redirection are also possible using pipes, and sensing of some interactions, e.g., \emph{tapping and grasping}, can be sensed acoustically.  Due to differential sound conductivity in different printed materials, solid pipes of a material with greater conductivity (i.e., rigid, high-density) can be embedded in a model of a lesser conductivity (i.e., softer).  A microphone or piezo placed at the system-side of these sound-conducting pipes can determine where the model was tapped and how it was tapped.  Active acoustic sensing as described in Touch \& Activate \cite{Ono-touchandactivate} is also possible; this technique would allow for particular areas of interest (connected to rigid pipes) to be touch sensitive and enable grasp sensing.

>>>>

The promise of 3D printing is two-fold: it enables the manufacturing of complex objects at low volumes, and it allows for the manufacturing of geometries that are impossible to create using traditional techniques like injection molding.  Printing pipes to prototype interactive objects exploits both advantages. Prototypes by definition are low-volume parts, and pipes require complex interior geometries that are very difficult or impossible to produce using other processes. Our work has focused on routing pipes that are manually filled after a print has completed. However, the fundamental operations of 3D path routing and topology specification that our tool offers will remain relevant as 3D printing technology advances. Multi-material printers are already available; as they advance and support the embedding of additional materials (e.g., conductors), \systemname can enable designers to efficiently specify where different functional materials should be placed at design time.

@@

\emph{Aural} outputs can be created with gases.  Pipes and cavities can act as resonators that can be leveraged to create 3D-printed sound chambers with explicitly designed sound characteristics~\cite{Zoran-flute} (see Figure \ref{fig:speculative}a).  %All that is necessary for this is an enclosed chamber with a pipe connected to it via a narrow neck-point (see Figure \ref{fig:ocarina}).  
Passive sound amplification and sound redirection are also possible using pipes, and sensing of some interactions, e.g., \emph{tapping and grasping}, can be sensed acoustically.  Due to differential sound conductivity in different printed materials, solid pipes of a material with greater conductivity (i.e., rigid, high-density) can be embedded in a model of a lesser conductivity (i.e., softer).  A microphone or piezo placed at the system-side of these sound-conducting pipes can determine where the model was tapped and how it was tapped.  Active acoustic sensing as described in Touch \& Activate \cite{Ono-touchandactivate} is also possible; this technique would allow for particular areas of interest (connected to rigid pipes) to be touch sensitive and enable grasp sensing.

### 2014-04-12 paper/exampleobjects.tex
bjoern's pass

The models we used for the toys were downloaded from the  Thingiverse website. We then used \systemname to create the desired internal pipes. All components were fabricated on a Makerbot, support-free.  After printing, we injected copper paint (CuPro-Cote) into the interior pipes using a craft syringe.  This paint requires approximately 2 days to fully dry in this configuration (3mm diameter tubes, maximum tube length 10cm).  Our smart base is powered by an Arduino Uno running open-source SFCS code\footnote{\url{http://www.instructables.com/id/Touche-for-Arduino-Advanced-touch-sensing}}.

@@

\subsection{Custom Radio (open, threadable, endpoint)}
A custom radio (figure \ref{fig:examples}c) shows how pipes can be used to integrate electronic components into the user-facing surface of an object. The radio includes a power and volume dial, and LED which goes on when the radio is on, and a tuner dial. An Arduino Pro Micro microcontroller, Si4703 FM tuner, and 6V (4xAA) power supply are embedded in the base of the radio. The sound is played through a single .5 Watt speaker. This shows a Midas-like \cite{Savage-midas} possibility: multiple terminals all routed back to a shared endpoint (in this case, the Arduino).

@@

\subsection{Presence-aware Pen Holder (open, threadable, endpoint)}
Our presence-aware pen holder can distinguish which tool or tools a user has picked up (see Figure \ref{fig:examples}d).  Our pen holder uses a modification of the FlyEye technique described by Wimmer \cite{Wimmer-flyeye} in which an IR camera senses a user's grasp on an object, getting data from IR light transmitted on fiber optic cables.  We marry this technique here with the Sauron technique \cite{Savage-sauron}: instead of using mirrors to redirect light and motion sensing as Sauron does, we use fiber optic cables.

The penholder body was created in Solidworks. We used \systemname to add four internal open pipes connecting each pen chamber to the based on the pen holder. This prototype was built by our Makerbot support-free.  Each pipe was then threaded with a fiber optic cable.  We use a single cable per pipe; our 6mm diameter fiber optic cables, in comparison to the fine tubes used in the original work, can send and receive through the same cable because their cross-sectional area is large enough to accommodate both functions. At the base of each tube is a QRE1113 line sensor digital breakout board, which has an integrated IR emitter and receiver.   When a pen is in its appointed place, the emitted infrared light is reflected off its bottom and travels back to the receiver, where it registers as bright.

@@

The maze is based on an SVG file we manually created and processed with our internal path routing tool.  We printed the maze on the Objet using a transparent material. The final artifact was fabricated in two halves fastened together via glue, to allow removal of support material with a high-pressure water tool.  We plugged the ends of the tubes post-print with additional material to ensure the ball does not escape.

@@

Neon art is traditionally made from hand-formed glass tubes containing neon gas.  The tubes light up when a current is passed through them.  For this type of art, the path of the tubes is of crucial importance, as it determines how the sign will look.  We designed a custom neon robot head which can be animated to ``talk''. 
The external geometry of the model was imported into \systemnamenospace, which created the associated pipes using its internal path routing tool.  We added additional endpoint-constrained tubes as exits out the rear of the model to allow us to hide the controls (see Figure \ref{fig:neon}B).  We then printed the model on the Objet using transparent material. The model was printed in two halves, cutting through the plane of internal path, to facilitate assembly.

>>>>

The models we used for the toys were downloaded from the  Thingiverse website. \bjoern{I thought the brain model came from Berkeley?} We then used \systemname to create the desired internal pipes. All components were fabricated on a Makerbot, support-free.  After printing, we injected copper paint (CuPro-Cote) into the interior pipes using a craft syringe.  This paint requires approximately 2 days to fully dry in this configuration (3mm diameter tubes, maximum tube length 10cm).  Our smart base is powered by an Arduino Uno running open-source SFCS code\footnote{\url{http://www.instructables.com/id/Touche-for-Arduino-Advanced-touch-sensing}}. \bjoern{If we don't have appendices, insert resistance measurement for this paint here.}

@@

\subsection{Custom Radio (open, threadable, endpoint)}
A custom radio (Figure \ref{fig:examples}c) shows how pipes can be used to integrate electronic components into the user-facing surface of an object. The radio includes a power and volume dial, and LED which goes on when the radio is on, and a tuner dial. An Arduino Pro Micro microcontroller, Si4703 FM tuner, and 6V (4xAA) power supply are embedded in the base of the radio. The sound is played through a single .5 Watt speaker. This shows a Midas-like \cite{Savage-midas} possibility : multiple terminals all routed back to a shared endpoint (in this case, the Arduino). \bjoern{last sentence is confusing. May not need Midas reference.}

@@

\subsection{Presence-aware Pen Holder (open, threadable, endpoint)}
Our presence-aware pen holder can distinguish which tool or tools a user has picked up (see Figure \ref{fig:examples}d).  Our pen holder uses a modification of the FlyEye technique described by Wimmer \cite{Wimmer-flyeye} in which an IR camera senses a user's grasp on an object, getting data from IR light transmitted on fiber optic cables.  We marry this technique here with the Sauron technique \cite{Savage-sauron}: instead of using mirrors to redirect light and motion sensing as Sauron does, we use fiber optic cables. \bjoern{I think people remember Sauron as being all about hollow objects and we use ray-tracing to know how reflected light will travel; using fiberoptics seems not that closely related, other than its use of optical sensors.}

The penholder body was created in Solidworks. We used \systemname to add four internal open pipes connecting each pen chamber to the based on the pen holder. This prototype was built on our Makerbot support-free.  Each pipe was then threaded with a fiber optic cable.  We use a single cable per pipe; our 6mm diameter fiber optic cables, in comparison to the fine tubes used in the original work, can emit and receive through the same cable because their cross-sectional area is large enough to accommodate both functions \bjoern{still unclear how this actually works; I'm a little worried about having any vague statements about fiber optics as Patrick could get this paper}. At the base of each tube is a QRE1113 line sensor digital breakout board, which has an integrated IR emitter and receiver.   When a pen is in its appointed place, the emitted infrared light is reflected off its bottom and travels back to the receiver, where it registers as bright.

@@

The maze is based on an SVG file we manually created and processed with our internal path routing tool.  We printed the maze on the Objet using a transparent material \bjoern{bottom doesn't look transparent. The final artifact was fabricated in two halves fastened together via glue, to allow removal of support material with a high-pressure water tool.  We plugged the ends of the tubes post-print with additional material to ensure the ball does not escape.

@@

Neon art is traditionally made from hand-formed glass tubes containing neon gas.  The tubes light up when a current is passed through them.  For this type of art, the path of the tubes is of crucial importance, as it determines how the sign will look.  We designed a custom neon robot head which can be animated to ``talk''. 
The external geometry of the model was imported into \systemnamenospace, which created the associated pipes using its internal path routing tool.  We added additional endpoint-constrained tubes as exits out the rear of the model to allow us to hide the controls (see Figure \ref{fig:neon}B).  We then printed the model on the Objet using transparent material. The model was printed in two halves, cutting through the plane of the internal path, to facilitate assembly.

### 2014-04-12 paper/relatedwork.tex
bjoern's pass

\subsubsection{Interaction for Fabrication vs. Fabrication for Interaction}
HCI researchers are also developing novel interaction techniques for providing input to digital fabrication machines~\cite{Mueller-constructable,Willis-interactive,mixfab}, and new hybrid hand tools combine manual processes with digital fabrication~\cite{zoran2013freed,rivers2012position}. These projects are complementary as they target different aspects of the design process, though it is conceivable that our pipe design tools could be added to augmented reality modeling interfaces like MixFab~\cite{mixfab}.

>>>>

\subsubsection{Interaction for Fabrication vs. Fabrication for Interaction}
HCI researchers are also developing novel interaction techniques for providing input to digital fabrication machines~\cite{Mueller-constructable,Willis-interactive,mixfab}, and new hybrid hand tools that combine manual processes with digital fabrication~\cite{zoran2013freed,rivers2012position}. These projects are complementary as they target different aspects of the design process, though it is conceivable that our pipe design tools could be added to augmented reality modeling interfaces like MixFab~\cite{mixfab}.
